SpecHunter: Interactively Inferring Taint Specifications Using Bayes Net

### 2021-04-04 My-Papers/SpecHunter/overview.tex
graph manipulation

Swan sucks: too much variance on its performance depending on dataset quality/quantity

@@

Let us first state with the data-flow schemas. In the above table, red cells
should contain very high probabilities, orange
cells should contain relatively high probabilities, whereas green cells should
be assigned low probabilities, and blue cells should be of very low probabilities.
The idea is this: by the definitions of ``source'', ``sanitizer'', and ``sink'',
data must flow from a source to a sink through possibly a sanitizer, but it
cannot flow in any other sequence of such methods. (For example, data cannot
possibly flow from a sink through a source to a sanitizer.) Also, we note that
any number of ``none'' methods, which are none of the three, can be interleaved
freely between a source and a sanitizer, and between a sanitizer and a sink.
Therefore, we encode these possibilities into a tabular form containing probabilities
like the above.

@@

Since Bayesian networks are directed acyclic graphs (DAGs), we need to eliminate
all cycles before we turn the splitted graphs into Bayesian networks. We first
use \emph{networkx}'s cycle
detection algorithm which pinpoints the set of edges forming a cycle by
searching the graph in a depth-manner for this task. We then randomly pick one of
such edges causing a cycle and delete it. Repeatedly applying the two
operations until the algorithm fails to detect a cycle, we transform the
splitted graphs into DAGs.      % TODO 이거 figure로 굳이 뺄 필요 없겠지...?

% 'incoming edge가 너무 많아서도, 너무 적어서도 안 된다.'
Next, we control the number of incoming edges of each node. It is already
mentioned that the size of a node's CPT is exponential to the number of its
parent nodes. To our empirical knowledge, if the number of incoming edges (hence
the number of parent nodes) becomes more than 6, the process of converting the
graph into a Bayesian network becomes drastically intractable. Therefore, we
use a simple algorithm to deal with those.

After all these processing, we are finally ready to turn chopped graphs into
small, yet full-blown Bayesian networks.

@@

Here, we expound on the core inference algorithm.

>>>>

% TODO
Swan sucks: too much variance on its performance depending on dataset quality/quantity

@@

Let us first start with the data-flow schemas. In the above table, red cells
should contain very high probabilities, orange
cells should contain relatively high probabilities, whereas green cells should
be assigned low probabilities, and blue cells should be of very low probabilities.
The idea is this: by the definitions of ``source'', ``sanitizer'', and ``sink'',
data must flow from a source to a sink through possibly a sanitizer, but it
cannot flow in any other sequence of such methods. (For example, data cannot
possibly flow from a sink through a source to a sanitizer.) Also, we note that
any number of ``none'' methods, which are none of the three, can be interleaved
freely between a source and a sanitizer, and between a sanitizer and a sink.
Therefore, we encode these possibilities into a tabular form containing probabilities
like the above.

@@

Since Bayesian networks are directed acyclic graphs (DAGs), we need to eliminate
all cycles before we turn the splitted graphs into Bayesian networks. We first
use \emph{networkx}'s cycle
detection algorithm which pinpoints the set of edges forming a cycle by
searching the graph in a depth-manner for this task. We then randomly pick one of
such edges causing a cycle and delete it. Repeatedly applying the two
operations until the algorithm fails to detect a cycle, we transform the
splitted graphs into DAGs.

% 'incoming edge가 너무 많아서도, 너무 적어서도 안 된다.'
Next, we control the number of incoming edges of each node. It is already
mentioned that the size of a node's CPT is exponential to the number of its
parent nodes. To our empirical knowledge, if the number of incoming edges (hence
the number of parent nodes) becomes more than 6, the process of converting the
graph into a Bayesian network becomes drastically intractable. Therefore, we
reduce the number of parents of such ``rich nodes'' by making the parents of the
rich node shoot a similarity edge not to the rich node in question, but to some
other node that is not yet rich.

Also, we minimize the number of ``isolated nodes'' that have no incoming edges
nor outgoing edges. Since these nodes' marginal probabilities are independent of
those of any other nodes, their marginals never get updated if any other nodes'
marginals get updated. Thus, they are one of the major factors that make the
inference inefficient. We control the number of isolated nodes of a splitted
graph by sticking the isolated node $n_1$ to a node $n_2$ of other graph if both
were connected in the initial graph either by edge $(n_1, n_2)$ or $(n_2, n_1)$.

After all these preprocessing, we are finally ready to turn chopped graphs into
small, yet full-blown Bayesian networks.

@@

Here, we expound on the core inference algorithm. The inference algorithm is
largely
